Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Consistency
A bit darker, for printing

\begin{figure}[b] % first page if possible
    \centering
    \begin{tikzpicture}[scale=0.33]%{{{
        \begin{scope}[rotate=90]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!40] (M4) -- (M6);
            \draw [color=uofgsandstone!40] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!40] (M6) -- (M7);
            \draw [color=uofgsandstone!40] (M6) -- (M8);
            \draw [color=uofgsandstone!40] (M6) -- (M9);
            \draw [very thick] (M7) -- (M9);
            \draw [very thick] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=7cm, rotate=90]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!40] (M4) -- (M6);
            \draw [color=uofgsandstone!40] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!40] (M6) -- (M7);
            \draw [very thick] (M7) -- (M8);
            \draw [very thick] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=18cm, rotate=90]
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [very thick] (M4) -- (M6);
            \draw [very thick] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!40] (M6) -- (M7);
            \draw [very thick] (M6) -- (M8);
            \draw [color=uofgsandstone!40] (M6) -- (M9);
            \draw [color=uofgsandstone!40] (M7) -- (M9);
            \draw [color=uofgsandstone!40] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=25cm, rotate=90]
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [very thick] (M4) -- (M6);
            \draw [very thick] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [very thick] (M6) -- (M7);
            \draw [draw=uofgsandstone!40] (M7) -- (M8);
            \draw [draw=uofgsandstone!40] (M8) -- (M9);
        \end{scope}
\end{tikzpicture}
\caption{A maximum common induced subgraph of the first two graphs has eight vertices, shaded.
However, if we require the common subgraph to be connected, only seven vertices may be
selected---one way to do this is shown in the third and fourth graphs.}\label{figure:mcsexample}
\end{figure}

@@

This CP model is improved by Ndiaye and Solnon \cite{DBLP:conf/cp/NdiayeS11} by replacing binary
difference constraints with a soft global allDifferent constraint which maximizes the number of
$x_u$ variables that are assigned to values different from $\bot$, while ensuring they are all
different when they are not assigned to $\bot$. They find that the combination ``MAC+Bound'' (resp.
``FC+Bound'') obtains the best results on labelled (resp. non labelled) graphs and outperforms the
two previous approaches. The combination ``MAC+Bound'' maintains arc consistency~\cite{sabi94} of
edge constraints, whereas the combination ``FC+Bound'' simply performs forward-checking on these
constraints. In both combinations, the ``Bound'' filtering checks whether it is possible to assign
distinct values to enough $x_u$ variables to surpass the best cost found so far (it is a weaker
version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum number of variables that
can be assigned distinct values).

@@

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[scale=0.33]%{{{
        \begin{scope}
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 8) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 6) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 6) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md) at (4, 6) {\phantom{0}};

@@

            \draw [very thick] (Mb) -- (Mc);
            \draw [very thick] (Mc) -- (Md);
            \draw [color=uofgsandstone!40] (Ma) -- (Mc);
            \draw [color=uofgsandstone!40] (Ma) to [out=150, in=80, looseness=8] (Ma);
            \draw [very thick] (Mb) to [out=150, in=80, looseness=8] (Mb);
        \end{scope}

        \begin{scope}
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (1, 2) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (M3) at (1, 0) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (3, 0) {\phantom{0}};

@@

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [color=uofgsandstone!40] (M3) -- (M4);
            \draw [color=uofgsandstone!40] (M1) -- (M3);

            \draw [color=uofgsandstone!40] (M3) to [out=280, in=210, looseness=8] (M3);
            \draw [very thick] (M1) to [out=150, in=80, looseness=8] (M1);
        \end{scope}

        \begin{scope}[xshift=15cm, yshift=-1cm]
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
            \node (La1) [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
            \node (La2) [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
            \node (La3) [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
            \node (La4) [above = 0 of Ma4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
            \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
            \node [left = 0 of Mb2, font=\small] { \vphantom{0}2 };
            \node [left = 0 of Mb3, font=\small] { \vphantom{0}3 };
            \node [left = 0 of Mb4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
            \node (Lc1) [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
            \node (Lc2) [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
            \node (Lc3) [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
            \node (Lc4) [below = 0 of Mc4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
            \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };
            \node [right = 0 of Md2, font=\small] { \vphantom{0}2 };
            \node [right = 0 of Md3, font=\small] { \vphantom{0}3 };
            \node [right = 0 of Md4, font=\small] { \vphantom{0}4 };

@@

            \begin{scope}[on background layer]
                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Md4.west)!0.5!(Md4)$);
                \draw [draw=uofgsandstone!40] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
                \draw [draw=uofgsandstone!40] ($(Ma3.south)!0.5!(Ma3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
                \draw [draw=uofgsandstone!40] ($(Mb3.east)!0.5!(Mb3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mc4.north)!0.5!(Mc4)$);
                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Ma3.south)!0.5!(Ma3)$);
                \draw [draw=uofgsandstone!40] ($(Md2.west)!0.5!(Md2)$) -- ($(Mb3.east)!0.5!(Mb3)$);
                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Md4.west)!0.5!(Md4)$);
                \draw [very thick] ($(Mc2.north)!0.5!(Mc2)$) -- ($(Md4.west)!0.5!(Md4)$);
        \end{scope}
        \end{scope}

@@

            \draw [draw=uofgsandstone!40] (Ma) -- (Mb);
            \draw [draw=uofgsandstone!40] (Ma) -- (Mc);
            \draw [draw=uofgsandstone!40] (Mb) -- (Mc);
            \draw [draw=uofgsandstone!40] (Mb) -- (Md);
            \draw [draw=uofgsandstone!40] (Mc) -- (Me);

@@

            \draw [color=uofgsandstone!40] (M1) -- (M2);
            \draw [color=uofgsandstone!40] (M1) -- (M3);
            \draw [color=uofgsandstone!40] (M2) -- (M4);
            \draw [color=uofgsandstone!40] (M3) -- (M4);

>>>>

\begin{figure}[b] % first page if possible
    \centering
    \begin{tikzpicture}[scale=0.33]%{{{
        \begin{scope}[rotate=90]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!60] (M4) -- (M6);
            \draw [color=uofgsandstone!60] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [color=uofgsandstone!60] (M6) -- (M8);
            \draw [color=uofgsandstone!60] (M6) -- (M9);
            \draw [very thick] (M7) -- (M9);
            \draw [very thick] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=7cm, rotate=90]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!60] (M4) -- (M6);
            \draw [color=uofgsandstone!60] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [very thick] (M7) -- (M8);
            \draw [very thick] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=18cm, rotate=90]
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [very thick] (M4) -- (M6);
            \draw [very thick] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [very thick] (M6) -- (M8);
            \draw [color=uofgsandstone!60] (M6) -- (M9);
            \draw [color=uofgsandstone!60] (M7) -- (M9);
            \draw [color=uofgsandstone!60] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=25cm, rotate=90]
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [very thick] (M4) -- (M6);
            \draw [very thick] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [very thick] (M6) -- (M7);
            \draw [draw=uofgsandstone!60] (M7) -- (M8);
            \draw [draw=uofgsandstone!60] (M8) -- (M9);
        \end{scope}
\end{tikzpicture}
\caption{A maximum common induced subgraph of the first two graphs has eight vertices, shaded.
However, if we require the common subgraph to be connected, only seven vertices may be
selected---one way to do this is shown in the third and fourth graphs.}\label{figure:mcsexample}
\end{figure}

@@

This CP model is improved by Ndiaye and Solnon \cite{DBLP:conf/cp/NdiayeS11} by replacing binary
difference constraints with a soft global allDifferent constraint which maximizes the number of
$x_u$ variables that are assigned to values different from $\bot$, while ensuring they are all
different when they are not assigned to $\bot$. They find that the combination ``MAC+Bound'' (resp.
``FC+Bound'') obtains the best results on labelled (resp. unlabelled) graphs and outperforms the
two previous approaches. The combination ``MAC+Bound'' maintains arc consistency~\cite{sabi94} of
edge constraints, whereas the combination ``FC+Bound'' simply performs forward-checking on these
constraints. In both combinations, the ``Bound'' filtering checks whether it is possible to assign
distinct values to enough $x_u$ variables to surpass the best cost found so far (it is a weaker
version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum number of variables that
can be assigned distinct values).

@@

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[scale=0.33]%{{{
        \begin{scope}
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 8) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 6) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 6) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md) at (4, 6) {\phantom{0}};

@@

            \draw [very thick] (Mb) -- (Mc);
            \draw [very thick] (Mc) -- (Md);
            \draw [color=uofgsandstone!60] (Ma) -- (Mc);
            \draw [color=uofgsandstone!60] (Ma) to [out=150, in=80, looseness=8] (Ma);
            \draw [very thick] (Mb) to [out=150, in=80, looseness=8] (Mb);
        \end{scope}

        \begin{scope}
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (1, 2) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (3, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (M3) at (1, 0) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (3, 0) {\phantom{0}};

@@

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [color=uofgsandstone!60] (M3) -- (M4);
            \draw [color=uofgsandstone!60] (M1) -- (M3);

            \draw [color=uofgsandstone!60] (M3) to [out=280, in=210, looseness=8] (M3);
            \draw [very thick] (M1) to [out=150, in=80, looseness=8] (M1);
        \end{scope}

        \begin{scope}[xshift=15cm, yshift=-1cm]
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
            \node (La1) [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
            \node (La2) [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
            \node (La3) [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
            \node (La4) [above = 0 of Ma4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
            \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
            \node [left = 0 of Mb2, font=\small] { \vphantom{0}2 };
            \node [left = 0 of Mb3, font=\small] { \vphantom{0}3 };
            \node [left = 0 of Mb4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
            \node (Lc1) [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
            \node (Lc2) [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
            \node (Lc3) [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
            \node (Lc4) [below = 0 of Mc4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!60, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
            \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };
            \node [right = 0 of Md2, font=\small] { \vphantom{0}2 };
            \node [right = 0 of Md3, font=\small] { \vphantom{0}3 };
            \node [right = 0 of Md4, font=\small] { \vphantom{0}4 };

@@

            \begin{scope}[on background layer]
                \draw [draw=uofgsandstone!60] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Md4.west)!0.5!(Md4)$);
                \draw [draw=uofgsandstone!60] ($(Ma1.south)!0.5!(Ma1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
                \draw [draw=uofgsandstone!60] ($(Ma3.south)!0.5!(Ma3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
                \draw [draw=uofgsandstone!60] ($(Mb3.east)!0.5!(Mb3)$) -- ($(Mc4.north)!0.5!(Mc4)$);
                \draw [draw=uofgsandstone!60] ($(Md2.west)!0.5!(Md2)$) -- ($(Mc4.north)!0.5!(Mc4)$);
                \draw [draw=uofgsandstone!60] ($(Md2.west)!0.5!(Md2)$) -- ($(Ma3.south)!0.5!(Ma3)$);
                \draw [draw=uofgsandstone!60] ($(Md2.west)!0.5!(Md2)$) -- ($(Mb3.east)!0.5!(Mb3)$);
                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Mc2.north)!0.5!(Mc2)$);
                \draw [very thick] ($(Mb1.east)!0.5!(Mb1)$) -- ($(Md4.west)!0.5!(Md4)$);
                \draw [very thick] ($(Mc2.north)!0.5!(Mc2)$) -- ($(Md4.west)!0.5!(Md4)$);
        \end{scope}
        \end{scope}

@@

            \draw [draw=uofgsandstone!60] (Ma) -- (Mb);
            \draw [draw=uofgsandstone!60] (Ma) -- (Mc);
            \draw [draw=uofgsandstone!60] (Mb) -- (Mc);
            \draw [draw=uofgsandstone!60] (Mb) -- (Md);
            \draw [draw=uofgsandstone!60] (Mc) -- (Me);

@@

            \draw [color=uofgsandstone!60] (M1) -- (M2);
            \draw [color=uofgsandstone!60] (M1) -- (M3);
            \draw [color=uofgsandstone!60] (M2) -- (M4);
            \draw [color=uofgsandstone!60] (M3) -- (M4);
